---
title: "Homework5 Submission3"
author: "Moyo Odugbemi"
prefer-html: true
subtitle: "https://github.com/modugbe/homework5"
format: 
   pdf: 
     df-print: default
     output-file: "odugbemi-m-hwk5-3"
     output-ext: "pdf"
     header-includes:
        - \usepackage{float}
        - \floatplacement{table}{H}
---


```{r results="hide", echo=FALSE, message=FALSE}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, 
               data.table, gdata, scales, kableExtra, modelsummary, fixest)
```



```{r results="hide", echo=FALSE, message=FALSE}
#| include: false
#| eval: true
 
load("/Users/moyosoreoluwaodugbemi/Econ 470/Homework 5/submission2/Hwk5_workspace.Rdata")
```


\newpage
#Question 1
```{r results="hide", echo=FALSE, message=FALSE}
number1
```

\newpage
#Question 2
The initial increase in self purchase resulted from the establishment of the exchange. However when the exchange lacked support by the Trump administration that started in 2016, we see a decrease in self purchase. One specific policy was the scale back of funding for navigators. That administration also reduced federal role in the ACA and transferred enrolment responsibility from the federal marketplace to private web brokers.
(https://www.commonwealthfund.org/blog/2018/affordable-care-act-under-trump-administration)

\newpage
#Question 3
```{r results="hide", echo=FALSE, message=FALSE}
number3
```

\newpage
#Question 4
```{r results="hide", echo=FALSE, message=FALSE}
number4
```

\newpage
#Question 5
```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
#| echo: false
#| label: DDtbl
#| tbl-cap: "DD Table for Medicaid Expansion"

options(knitr.kable.NA = 0)
knitr::kable(dd_table, 
          booktabs = TRUE) %>%
          kable_styling(latex_options=c("scale_down"))
```

\newpage
#Question 6

```{r results="asis", echo=FALSE, message=FALSE}
#| echo: false
#| label: tbl-ddregs
#| tbl-cap: "DD Estimates for Medicaid Expansion"

modelsummary(number6,
             coef_rename=c("postTRUE" = "Post 2014","expand_everTRUE"="Expand",
                           "treat" = "Post x Expand"),
             gof_omit='DF|F|Lik|AIC|BIC|Adj') %>%
    kable_styling(latex_options="hold_position")
```


\newpage
#Question 7 
```{r echo=FALSE, message=FALSE}
#| echo: false
#| label: tbl-ddregs2
#| tbl-cap: "DD Estimates for Medicaid Expansion with TWFE"

models <- list("Standard DD" = number6, 
               "TWFE" = number7)
modelsummary(models,
             coef_rename=c("postTRUE" = "Post 2014","expand_everTRUE"="Expand",
                           "treat" = "Post x Expand"),
             gof_omit='DF|F|Lik|AIC|BIC|Adj') %>%
    kable_styling(latex_options="hold_position")
```


\newpage
#Question 8 
```{r echo=FALSE, message=FALSE}
#| echo: false
#| label: tbl-ddregs3
#| tbl-cap: "DD Estimates for Medicaid Expansion with Staggered Treatment"

models <- list("Standard DD" = number6, 
               "TWFE" = number7,
               "Time-varying Treatment" = number8)
modelsummary(models,
             coef_rename=c("postTRUE" = "Post 2014","expand_everTRUE"="Expand",
                           "treat" = "Post x Expand"),
             gof_omit='DF|F|Lik|AIC|BIC|Adj') %>%
    kable_styling(latex_options="hold_position")
```

\newpage
#Question 9 
```{r results="hide", echo=FALSE, message=FALSE}
#| echo: false
#| label: fig-eventstudy1
#| fig-cap: "Event Study with Common Treatment Time"

iplot(mod.twfe, 
      xlab = 'Time to treatment',
      main = '')
```

\newpage
#Question 10
```{r results="hide", echo=FALSE, message=FALSE}
iplot(mod.twfe2, 
      xlab = 'Time to treatment',
      main = '')
```